Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-19 Paper.tex
Clarify minor point on hash collisions. Fixed #7.

\subsection{Trie Database}
Thus no explicit assumptions are made concerning what data is stored and what is not, since that is an implementation-specific consideration; we simply define the identity function mapping the key-value set $\mathfrak{I}$ to a 32-byte hash and assert that only a single such hash exists for any $\mathfrak{I}$, which though not strictly true is accurate within acceptable precision. In reality, a sensible implementation will not fully recompute the trie root hash for each set.

>>>>

\subsection{Trie Database}
Thus no explicit assumptions are made concerning what data is stored and what is not, since that is an implementation-specific consideration; we simply define the identity function mapping the key-value set $\mathfrak{I}$ to a 32-byte hash and assert that only a single such hash exists for any $\mathfrak{I}$, which though not strictly true is accurate within acceptable precision given the SHA3 hash's collision resistance. In reality, a sensible implementation will not fully recompute the trie root hash for each set.
